Re-run, Repeat, Reproduce, Reuse, Replicate:\\Transforming Code into Scientific Contributions

### 2017-08-25 draft.tex
Typos, more compact layout.

\title{Re-run, Repeat, Reproduce, Reuse, Replicate:\\Transforming Code into Scientific Contributions}
% \title{Run Python, run!}
% \title{The R Quintuplet (R$^5$)}
% \author{Nicolas P. Rougier and Fabien C. Y. Benureau}
\author{
  \textbf{Fabien C. Y. Benureau}$^{1,2,3,*}$,
  \textbf{Nicolas P. Rougier}$^{1,2,3}$\\ \begin{minipage}{\textwidth}
    \begin{center}
      \vspace{2mm}
      $^{1}$INRIA Bordeaux Sud-Ouest Talence, France $^{2}$ Institut des
      Maladies Neurodégénératives, Université de Bordeaux, CNRS UMR 5293,
      Bordeaux, France $^{3}$ LaBRI, Université de Bordeaux, Bordeaux INP, CNRS
      UMR 5800, Talence, France\\
      \vspace{2mm}
      $^{*}$Corresponding author:
      \href{mailto:fabien.benureau@gmail.com}{fabien.benureau@gmail.com}
    \end{center}
  \end{minipage}
}
\date{}

@@

Documentation is one of the most potent tools for reusability. A proper documentation on how to install and run the software often makes the difference whether other researchers manage to use it or not. A comment describing what each function does, however evident, can avoid hours of head-scratching. Great code may need few comments. Scientists, however, are not always brilliant developers. Of course, bad, complicated code should be rewritten until is simple enough to explain itself. But realistically, this is not always going to be done: there is simply not enough incentive for it. There, a comment that explains the intentions and reasons behind a block of code can tremendously useful.\\

@@

A researcher seeking to replicate published results might first consider only the article. If she fails to replicate the results, she will consult the original code, and be able to pinpoint why her code and the code of the authors differ in behavior. Because a mistake on their part? Hers? Or a difference in seemingly innocuous implementation details? A fine analysis of why a particular algorithmic description is lacking or ambiguous or why a minor implementation decision is in fact crucial to obtain the published results is of great  scientific value. Such an analysis can only be done with access to both the article and the code. With only the article, the researcher will often be unable to understand why she failed to replicate the results, and will naturally be inclined to only report replication successes.\\

@@

Making code reusable is a stretch goal that can yield tremendous benefits for you, your team and other researchers. Taken into account during development rather than as an afterthought, simple measures can avoid hours of head-scratching for others, and for yourself—in a few years. Documentation is paramount here, even if it is a single comment per function, as was done in the R$^4$ (reusable) version.\\

Finally, there is the belief that an article should suffice itself: the description of the algorithms present in the paper should suffice to re-obtain (to replicate) the published results. For well-written papers that precisely dissociate conceptually significant details from irrelevant implementation details, that may be. But science should not assume the best of cases. Science assumes that errors are ubiquitous. Every paper is a mistake or a forgotten parameter away from irreproducibility. Replication efforts use the paper first, and then the reproducible code that comes along with it whenever the paper falls short of being precise enough to be reimplemented.\\

>>>>

\title{Re-run, Repeat, Reproduce, Reuse, Replicate:\\Transforming Code into Scientific Contributions}
% \title{Run Python, run!}
% \title{The R Quintuplet (R$^5$)}
% \author{Nicolas P. Rougier and Fabien C. Y. Benureau}
\author{
  \textbf{Fabien C. Y. Benureau}$^{1,2,3,*}$,
  \textbf{Nicolas P. Rougier}$^{1,2,3}$\\ \begin{minipage}{0.8\textwidth}
    \begin{center}
      \vspace{2mm}
      \small
      $^{1}$INRIA Bordeaux Sud-Ouest Talence, France $^{2}$ Institut des
      Maladies Neurodégénératives, Université de Bordeaux, CNRS UMR 5293,
      Bordeaux, France $^{3}$ LaBRI, Université de Bordeaux, Bordeaux INP, CNRS
      UMR 5800, Talence, France\\
      \vspace{2mm}
      $^{*}$Corresponding author:
      \href{mailto:fabien.benureau@gmail.com}{fabien.benureau@gmail.com}
    \end{center}
  \end{minipage}
}
\date{}

@@

Documentation is one of the most potent tools for reusability. A proper documentation on how to install and run the software often makes the difference whether other researchers manage to use it or not. A comment describing what each function does, however evident, can avoid hours of head-scratching. Great code may need few comments. Scientists, however, are not always brilliant developers. Of course, bad, complicated code should be rewritten until is simple enough to explain itself. But realistically, this is not always going to be done: there is simply not enough incentive for it. There, a comment that explains the intentions and reasons behind a block of code can be tremendously useful.\\

@@

A researcher seeking to replicate published results might first consider only the article. If she fails to replicate the results, she will consult the original code, and with it be able to pinpoint why her code and the code of the authors differ in behavior. Because a mistake on their part? Hers? Or a difference in a seemingly innocuous implementation detail? A fine analysis of why a particular algorithmic description is lacking or ambiguous or why a minor implementation decision is in fact crucial to obtain the published results is of great scientific value. Such an analysis can only be done with access to both the article and the code. With only the article, the researcher will often be unable to understand why she failed to replicate the results, and will naturally be inclined to only report replication successes.\\

@@

Making code reusable is a stretch goal that can yield tremendous benefits for you, your team and other researchers. Taken into account during development rather than as an afterthought, simple measures can avoid hours of head-scratching for others, and for yourself—in a few years. Documentation is paramount here, even if it is a single comment per function, as it was done in the R$^4$ (reusable) version.\\

Finally, there is the belief that an article should suffice by itself: the descriptions of the algorithms present in the paper should suffice to re-obtain (to replicate) the published results. For well-written papers that precisely dissociate conceptually significant aspects from irrelevant implementation details, that may be. But scientific practice should not assume the best of cases. Science assumes that errors can crop up everywhere. Every paper is a mistake or a forgotten parameter away from irreproducibility. Replication efforts use the paper first, and then the reproducible code that comes along with it whenever the paper falls short of being precise enough to be reimplemented.\\
